ZCB Pricing

### 2018-08-07 ZCB Pricing .Rmd
Graphics

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[4,2:9], col="red",type = "p")
lines(1:8, senses[5,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p")
lines(1:8, senses[7,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[8,2:9], col="red",type = "p")
lines(1:8, senses[9,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01", "alpha=0.08", "alpha=0.16"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Beta")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[10,2:9], col="red",type = "p")
lines(1:8, senses[11,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("beta=0.1", "beta=0.8", "beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[12,2:9], col="red",type = "p")
lines(1:8, senses[13,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
```

@@

```{r 14}
# Convergence Tests for finite difference methods
# Varying rate steps

# rate_step <- c(0.02,0.016,0.012,0.010,0.008,0.006,0.005,0.004,0.003,0.002)
# rate_vec <- NULL
# for (i in 1:length(rate_step)){
#   rate_vec[i] <- length(seq(-0.4,0.6,rate_step[i])) 
# }
# 
# 
# closed_r <- NULL
# CN_conv_1 <- NULL
# Impl_conv_1 <- NULL
# Expl_conv_1 <- NULL
# 
# 
# 
# for (i in 1:length(rate_step)){
#   closed_r[i] <- bond_price()
# }
# 
# for (i in 1:length(rate_step)){
#   CN_conv_1[i] <- CN(J = seq(-0.4,0.6,rate_step[i]))
# }
# 
# for (i in 1:length(rate_step)){
#   Impl_conv_1[i] <- implicit(J = seq(-0.4,0.6,rate_step[i]))
# }
# 
# for (i in 1:length(rate_step)){
#   Expl_conv_1[i] <- explicit(J = seq(-0.4,0.6,rate_step[i]))
# }
# 
# par(mfrow = c(1,1))
# plot(closed_r, x = rate_vec, type = "l", xlab = "Number of time steps", ylab = "Estimated Price")
# lines(x = rate_vec, y = CN_conv_1, type = "l", lty = 2)
# lines(x = rate_vec, y = Impl_conv_1, type = "l", lty = 3, col = "blue")
# lines(x = rate_vec, y = Expl_conv_1, type = "l", lty = 4, col = "red")
# legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)

```{r 15}
# Covergence tests for Monte Carlo functions

>>>>

senses[1,1]="-"
senses[2,1]="r=0.05"
senses[3,1]="r=0.1"
senses[4,1]="T=1"
senses[5,1]="T=10"
senses[6,1]="sigma=0.001"
senses[7,1]="sigma=0.01"
senses[8,1]="alpha=0.01"
senses[9,1]="alpha=0.16"
senses[10,1]="beta=0.1"
senses[11,1]="beta=1.6"
senses[12,1]="alpha=0.01,beta=0.1"
senses[13,1]="alpha=0.16,beta=1.6"

@@

plot(x=1:8,y=senses[1,2:9], ylim =c(-0.4,1.4), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[4,2:9], col="red",type = "p", pch = 19)
lines(1:8, senses[5,2:9],col ="blue",type = "p", pch = 19)
legend("bottomright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)

plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p", pch = 19)
lines(1:8, senses[7,2:9],col ="blue",type = "p", pch = 19)
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)

plot(x=1:8,y=senses[1,2:9], ylim =c(-0.4,1.4), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[8,2:9], col="red",type = "p",pch = 19)
lines(1:8, senses[9,2:9],col ="blue",type = "p",pch = 19)
legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01", "alpha=0.08", "alpha=0.16"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)

plot(x=1:8,y=senses[1,2:9], ylim =c(-0.4,1.4), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Beta", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[10,2:9], col="red",type = "p",pch = 19)
lines(1:8, senses[11,2:9],col ="blue",type = "p",pch = 19)
legend("bottomright", inset = c(-0,0), legend = c("beta=0.1", "beta=0.8", "beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)

plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta",  xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[12,2:9], col="red",type = "p",pch = 19)
lines(1:8, senses[13,2:9],col ="blue",type = "p",pch = 19)
legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)
```

@@

```{r 14}
# Covergence tests for Monte Carlo functions
